Papers

### 2024-09-20 papers.qmd
update

-   Panagiotidi, M., Zavlis, O., Jones, M., & Stafford, T. (2023). [The three-dimensional community structure of ADHD traits captured by the ASRS scale: An Exploratory Graph Analysis](http://doi.org/10.1002/mpr.1997). International Journal of Methods in Psychiatric Research.  http://doi.org/10.1002/mpr.1997

@@

@@

-   Jones, A., Stafford, T., & Petrovskaya, E. (under review). [Exploring the multiverse of analysis options for the Addiction Stroop](https://psyarxiv.com/prfu2/).

@@

- Boag, R. J., Innes, R. J., Stevenson, N., Bahg, G., Busemeyer, J. R., Cox, G. E., … Forstmann, B. (2024, July 2). [An expert guide to planning experimental tasks for evidence accumulation modelling](https://osf.io/preprints/psyarxiv/snqgp). https://doi.org/10.31234/osf.io/snqgp

-   Adinugroho, I., Stafford, T., & Bentall, R. (2023, November 1). [The correlation between conspiracy mentality and vaccine intentions is moderated by social events: Evidence from longitudinal data during COVID-19 pandemic in the UK](https://osf.io/preprints/psyarxiv/5wcnz/). Retrieved from osf.io/preprints/psyarxiv/5wcnz

@@

-   Copeland, A., Stafford, T., & Field, M. (2023, August 23). [Value-based decision-making in regular alcohol consumers following experimental manipulation of alcohol value](https://osf.io/wcks6/). https://doi.org/10.31219/osf.io/wcks6

-   Panagiotidi, M., Zavlis, O., Jones, M., & Stafford, T. (2023, July 14). [The three-dimensional community structure of ADHD traits captured by the ASRS scale: An Exploratory Graph Analysis](https://psyarxiv.com/sakn9). Retrieved from psyarxiv.com/sakn9

@@

-   Jones, A., Stafford, T., & Petrovskaya, E. (2022). [Exploring the multiverse of analysis options for the Addiction Stroop](https://psyarxiv.com/prfu2/).

-   Panagiotidi, M., Stafford, T., and Overton, P. (submitted). The relationship between cognitive control and task switching and problematic phone use. [Email for document]

@@

>>>>

-    Panagiotidi, M., Zavlis, O., Jones, M., & Stafford, T. (2024). [The three-dimensional community structure of attention-deficit hyperactivity disorder (ADHD) traits captured by the Adult ADHD Self-Report Scale: An exploratory graph analysis](https://onlinelibrary.wiley.com/doi/full/10.1002/mpr.1997). International Journal of Methods in Psychiatric Research, e1997. <https://doi.org/10.1002/mpr.1997> - [[preprint](https://psyarxiv.com/sakn9)]

@@

-   Bannard, C., Leriche, M., Bandmann, O., Brown, C., Ferracane, E., Sánchez-Ferro, A., Obeso, J., Redgrave, P. and Stafford, T. (2019). [Reduced habit-driven errors in Parkinson's Disease](https://www.nature.com/articles/s41598-019-39294-z). Nature Scientific Reports 9(1), 3423. [[pre-print](https://psyarxiv.com/b25tf/)]

@@

-   Jones, A., Petrovskaya, E., & Stafford, T. (2024). [Exploring the multiverse of analysis options for the alcohol Stroop](https://link.springer.com/article/10.3758/s13428-024-02377-5). Behavior Research Methods, 56(4), 3578-3588. [[preprint](https://psyarxiv.com/prfu2/)]

@@

- Karadzhov, G., Vlachos, A., & Stafford, T. (2024). The effect of diversity on group decision-making. arXiv preprint [arXiv:2402.01427](https://arxiv.org/abs/2402.01427).

- Boag, R. J., Innes, R. J., Stevenson, N., Bahg, G., Busemeyer, J. R., Cox, G. E., … Forstmann, B. (2024, July 2). [An expert guide to planning experimental tasks for evidence accumulation modelling](https://osf.io/preprints/psyarxiv/snqgp).

@@

@@

@@

## 2024

-   Jones, A., Petrovskaya, E., & Stafford, T. (2024). [Exploring the multiverse of analysis options for the alcohol Stroop](https://link.springer.com/article/10.3758/s13428-024-02377-5). Behavior Research Methods, 56(4), 3578-3588. [[preprint](https://psyarxiv.com/prfu2/)]

-  Stafford, T., Gordon, H., Zhu, J., & Dommett, K. (2024). [Online political adverts: The effect of disclosures and opportunities for clandestine campaigning](https://onlinelibrary.wiley.com/doi/10.1111/pops.13034). Political Psychology, 00, 1–27. <https://doi.org/10.1111/pops.13034>

-    Panagiotidi, M., Zavlis, O., Jones, M., & Stafford, T. (2024). [The three-dimensional community structure of attention-deficit hyperactivity disorder (ADHD) traits captured by the Adult ADHD Self-Report Scale: An exploratory graph analysis](https://onlinelibrary.wiley.com/doi/full/10.1002/mpr.1997). International Journal of Methods in Psychiatric Research, e1997. <https://doi.org/10.1002/mpr.1997> [[preprint](https://psyarxiv.com/sakn9)]

-   Adinugroho, I., Stafford, T., & Bentall, R. (2024). [The correlation between conspiracy mentality and vaccine intentions is moderated by social events: Evidence from longitudinal data during COVID-19 pandemic in the UK](https://www.sciencedirect.com/science/article/pii/S0264410X24005103). Vaccine, 42(16), 3607-3614. <https://doi.org/10.1016/j.vaccine.2024.04.071>  [[preprint](https://osf.io/preprints/psyarxiv/5wcnz/)]

-   Copeland, A., Stafford, T., & Field, M. (2024). [Value-based decision-making in regular alcohol consumers following experimental manipulation of alcohol value](https://www.sciencedirect.com/science/article/pii/S0306460324001187). Addictive Behaviors, 156, 108069. <https://doi.org/10.1016/j.addbeh.2024.108069> [[preprint](https://osf.io/wcks6/)]
